---
title: "HW4"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rstan)
library(mnormt)
options(mc.cores = parallel::detectCores())
set.seed(03012021)
```

## Spatial Regression

Recall the Washington, DC dataset from HW 2. Consider a subset that contains only houses in `Good` condition, with one bathroom, and two bedrooms. Note that `LANDAREA` corresponds to the size of the lot, not the square footage of the apartment.

```{r, message = F}
DC <- read_csv('https://raw.githubusercontent.com/Stat534/homework_four/main/DC_wcoords.CSV')
```

#### 1. Spatial EDA (10 points)

Work through a descriptive and annotated Spatial Exploratory Data Analysis. This should parallel the class notes, but I expected a paragraph description, at a minimum, of the takeaway points for each part of the Spatial EDA.

#### 2. Spatial Data Analysis (10 points)

Similar to the spatial data analysis we completed as a demo, analyze the housing data. Use at least covariate in the mean structure. Then compare your spatial model to one without any spatial structure (this could be a mean-only model or something from lm). __Note: this comparison will require defining a metric__

#### 3. Exploring alternative spatial structure (5 points)

Now compare the spatial model from part 2 (presumably using exponential covariance structure), with a different spatial structure.

